---
title: "Sea Ice Depth/Thickness"
author: "Elnora Gaiser"
subtitle: null
---

# Introduction
Climate change has been a large topic of concern for many years now and one major impact that is occuring due to climate change is the drastic change in sea ice and glaciers. As Earth gets warmer, snap caps and sea ice are melting faster that many could've imagined. This project will hopefully help depict how much this has changed in recent years.  

# Materials and methods

Narrative and most code will go here.  Describe what you are doing and show how to do it (with code).

Install Packages:

```{r, message=F, warning=F}

library(rnoaa)
library(ggplot2)
library(tidyverse)

```

Downloading the Data:

* We will be using data from NOAA
* We will also be using data that is in the tidyverse.

```{r, message=F, warning=F}

url <- sidads.colorado.edu/pub/DATASETS/NOAA/G02172/
seaice(url)

```


```{r, message=F, warning=F}

```


# Results

Show tables, plots, etc. and describe them.

```{r}

```

# Conclusions

What have you learned?  Are there any broader implications?

# References

